Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-03-26 awipev-CO2.Rmd
sal_fb + temp_fb added to discrete df to convert spectro durafet

@@

# Conversion of spectro pH to a same T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet))
pH_seafet <- pH_seafet %>%
  dplyr::mutate(pH_s_seafet_temp_insitu = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_field, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$salinity_field,Pt=0,Sit=0))

pH_durafet <- d %>%
  dplyr::filter(!is.na(pH_s_durafet))
pH_durafet <- pH_durafet %>%
  dplyr::mutate(pH_s_durafet_temp_insitu = pHinsi(pH=pH_durafet$pH_s_durafet,ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_field, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$salinity_field,Pt=0,Sit=0))

# create separate seafet/durafet df to join to initial "d" df
pH_seafet_mean <- pH_seafet%>%
  dplyr::select(datetime,pH_s_seafet_temp_insitu)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(pH_s_seafet_temp_insitu = mean(pH_s_seafet_temp_insitu, na.rm = T))
pH_durafet_mean <- pH_durafet%>%
  dplyr::select(datetime,pH_s_durafet_temp_insitu)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(pH_s_durafet_temp_insitu = mean(pH_s_durafet_temp_insitu, na.rm = T))

#  make means in "d" to have same format and call it "discrete"
discrete <- d %>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(sal = mean(salinity_field, na.rm = T),
            temp = mean(temp_field, na.rm = T),
            at_mean_interp = mean(at_mean_interp, na.rm = T),
            at = mean(at, na.rm = T),
            qflag_at = mean(qflag_at, na.rm = T),
            ct_mean_interp = mean(ct_mean_interp, na.rm = T),
            ct = mean(ct, na.rm = T),
            qflag_ct = mean(qflag_ct, na.rm = T)
            )
# join discrete + seafet/durafet
discrete <- left_join(discrete, pH_seafet_mean, by='datetime')
discrete <- left_join(discrete, pH_durafet_mean, by='datetime')

##   *****Attention, temp noted by logisticians in d is FB temp with SBE45 ******
##   *****Attention, I asked to the logisticians to log outside temp from 9 june 2019

@@

carb <- carb(15, discrete$at*1e-6, discrete$ct*1e-6,S=discrete$sal, T=discrete$temp, P=0, Pt=0, Sit=0,k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")
discrete$phcalc<- carb$pH
discrete$pco2calc<- carb$pCO2
```

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
         AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
         #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
         #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
         ) %>%
  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu_11m=temp_insitu_11m_filtered, sal_fb = sal_fb_filtered, sal_insitu_ctd = sal_insitu_ctd_filtered, temp_fb = temp_fb_filtered, temp_insitu_ctd = temp_insitu_ctd_filtered, temp_sf=T_seaF)
```

```{r Combine discrete and continous data, echo=FALSE}
d_all <- d_hour #d_all will be the merger
d_all<- d_all%>%
  dplyr::mutate(month = month(month(datetime)))
# at
closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
discrete$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
# remove the drop_na() because of seafet/durafet line with na
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, at, qflag_at) %>%
    dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

# seaFET pH 
# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
# discrete$closest_datetime <- d_all$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pH_s_seafet_temp_insitu) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")
# #voltINT
# discrete2merge <- discrete %>%
#   #drop_na() %>%
#   dplyr::select(closest_datetime, voltINT) %>%
#   rename(datetime=closest_datetime)
# d_all <- full_join(d_all, discrete2merge, by="datetime")
# #voltEXT
# discrete2merge <- discrete %>%
#   #drop_na() %>%
#   dplyr::select(closest_datetime, voltEXT) %>%
#   rename(datetime=closest_datetime)
# d_all <- full_join(d_all, discrete2merge, by="datetime")

# duraFET pH 
# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
# discrete$closest_datetime <- d_all$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pH_s_durafet_temp_insitu) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

sal_xts <- dplyr::select(d_all, datetime, sal_mix)

@@

dygraph(sal_xts, group = "awipev", main="Salinity", ylab="Salinity") %>%
      dySeries("sal_mix", color = "blue", strokeWidth = 0, label = "S") %>%

@@

temp_insitu_xts <- dplyr::select(d_all, datetime, temp_mix)

@@

      dySeries("temp_mix", color = "blue", strokeWidth = 0, label = "T") %>%

@@

durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_insitu)

@@

    dySeries("pH_s_durafet_temp_insitu", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%

@@

seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_insitu)

@@

dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%

@@

  dySeries("pH_s_seafet_temp_insitu", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%

@@

# at_contros_cleaned_xts <- dplyr::select(d_all, datetime,sal_fb,sal_insitu_ctd)
# at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
# dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
#    #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
#   #dySeries("AT_filtered2", color = RColorBrewer::brewer.pal(4, "Set2"), strokeWidth = 0, pointSize=2) %>%
#   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
#   dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) 
#

p_sal_fb_sal_insitu<-  ggplot(d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),aes(x=sal_insitu_ctd, y= sal_fb, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  #geom_line(aes(x = sal_fb, y = sal_fb), linetype = "dashed") +
  geom_abline(slope=1, intercept=0, linetype = "dashed")+
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
  labs(title = paste("","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + #
  coord_fixed(ratio = 1 )+
   scale_colour_discrete(guide="none") +
  labs( x="Salinity CTD > 8 m", y="Salinity FB ", color = "Months") +theme_bw()
print(p_sal_fb_sal_insitu)

@@

# # PLOT
# seafet_contros_xts <- dplyr::select(d_all, datetime, temp_insitu_11m, temp_insitu_ctd, pressure_insitu_ctd_filtered, temp_mix, sal_mix)
# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
# dySeries("temp_insitu_11m", label = "temp_insitu_11m", color ="red",axis= "y2", strokeWidth=0, pointSize=4) %>%
# dySeries("temp_insitu_ctd", label = "temp_insitu_ctd", color ="blue",axis= "y2", strokeWidth=0, pointSize=3) %>%
# dySeries("temp_mix", label = "temp_mix", color ="green",axis= "y2", strokeWidth=0, pointSize=2) %>%
# dySeries("sal_mix", label = "sal_mix", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
# dySeries("pressure_insitu_ctd_filtered", label = "pressure_insitu_ctd_filtered", color ="black", strokeWidth=0, pointSize=2) %>%
#   dyLegend(show = "onmouseover")   %>%
#   #dyAxis( "y2",valueRange = c(-3, 36))%>%
#   dyAxis( "y2",valueRange = c(-3, 36))%>%
#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
#   dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
#   dyRangeSelector(height = 30, dateWindow= NULL)

@@

p<-  ggplot(d_all,aes(x=temp_insitu_11m, y= temp_fb, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_line(aes(x = temp_fb, y = temp_fb), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("T FB vs T insi","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
  labs( x="T insi", y="T FB ", color = "Months")  +theme_bw()
print(p)

d_all$diff_T_fb_insitu <- d_all$temp_sf - d_all$temp_insitu_11m
mean_diff_T_fb_insitu <- round(mean(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
sd_diff_T_fb_insitu <- round(sd(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
```

The mean difference between T seaFET and in situ is: `r mean_diff_T_fb_insitu` ± `r sd_diff_T_fb_insitu`°C.

@@

p<-  ggplot(d_all,aes(x=temp_insitu_ctd, y= temp_insitu_11m, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_line(aes(x = temp_insitu_11m, y = temp_insitu_11m), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("T FB vs T insi","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
  labs( x="T insi", y="T FB ", color = "Months")  +theme_bw()
print(p)

d_all$diff_T_fb_insitu <- d_all$temp_sf - d_all$temp_insitu_ctd
mean_diff_T_fb_insitu <- round(mean(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
sd_diff_T_fb_insitu <- round(sd(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
```

@@

# # We decided to calibrate pH data within each pH spectro measurement.
# # Thus, each pH spectro is taken as one calibration periode. 
# # We calculate here the day between 2 pH spectro in order to have the start/end of one deployment period.
# sfPeriod <- d_all%>%
#   dplyr::select(datetime, pH_s_seafet_temp_insitu)%>%
#   dplyr::filter(!is.na(pH_s_seafet_temp_insitu))
# # Remove pH spectro that not allow a calibration because of missing calibration value (voltINT, Sal or Temp insi)
# sfPeriod <- sfPeriod%>%
# dplyr::filter(datetime != "2018-04-16 07:00:00" & datetime != "2018-12-14 09:00:00" & datetime != "2019-01-18 09:00:00")
# 
# sfPeriod <-  sfPeriod %>%
#   dplyr::arrange(datetime) %>%
#   dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(sfPeriod)])/2* 3600)))%>%
#   dplyr::mutate(sf_interval = datetime + middle[2:nrow(sfPeriod)])
# 
# #put interval in a list with the start date of seaFET measurements
# sfinterv <- c( as_datetime("2017-08-24 13:00:00"), sfPeriod[,4])
# #Change period sfinterv[5]. make the end of this period longer until 2018-03-21 23:59:00 
# # This is needed in order to take in consideration pH from March 2018 with a calibration E0 lower (-1.4) than the next period (-0.38).
# sfinterv[5] <- ymd_hms("2018-03-22 23:59:59")
# #  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
# # sfinterv[6] <- ymd_hms("2018-04-24 18:00:00")
# #  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
# # sfinterv[14] <- ymd_hms("2019-01-29 16:00:00")
# 
# #sfinterv <-sort(unlist(sfinterv, use.names=FALSE))
# # set deployment period between 2 spectro measurements.

@@

# test <- d_all%>%
#   dplyr::filter(datetime=="2017-08-24 14:00:00")

>>>>

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
         AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
         #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
         #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
         ) %>%
  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered, temp_durafet = HW_Temperature1_filtered, temp_insitu_11m=temp_insitu_11m_filtered, sal_fb = sal_fb_filtered, sal_insitu_ctd = sal_insitu_ctd_filtered, temp_fb = temp_fb_filtered, temp_insitu_ctd = temp_insitu_ctd_filtered, temp_sf=T_seaF)

d_all <- d_hour #d_all will be the merger
d_all<- d_all%>%
  dplyr::mutate(month = month(month(datetime)))

@@

# add sal_fb + sal_insitu_ctd + temp_fb + temp_insitu_ctd from d_hour TO d, to use pHinsi
# use the closest time to add them
closest <- which.closest(d$datetime, d_all$datetime) # closest date and time
d$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
d$closest_datetime[abs(d$datetime - d_all$datetime[closest]) > 30*60] <- NA
# create closest_datetime in d_all (copy of datetime)
d_all$closest_datetime <- d_all$datetime
d <- left_join(d, d_all%>%dplyr::select(c(closest_datetime, sal_fb, temp_fb, sal_insitu_ctd, temp_insitu_ctd)), by="closest_datetime")

# Conversion of spectro pH to a same T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet)& !is.na(sal_insitu_ctd) )
pH_seafet <- pH_seafet %>%
  dplyr::mutate(pH_s_seafet_temp_ctd = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_insitu_ctd, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_insitu_ctd,Pt=0,Sit=0))

pH_durafet <- d %>%
  dplyr::filter(!is.na(pH_s_durafet))
pH_durafet <- pH_durafet %>%
  dplyr::mutate(pH_s_durafet_temp_fb = pHinsi(pH=pH_durafet$pH_s_durafet, ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_fb, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$sal_fb,Pt=0,Sit=0))

# create separate seafet/durafet df to join to initial "d" df
pH_seafet_mean <- pH_seafet%>%
  dplyr::select(datetime,pH_s_seafet_temp_ctd)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(pH_s_seafet_temp_ctd = mean(pH_s_seafet_temp_ctd, na.rm = T))
pH_durafet_mean <- pH_durafet%>%
  dplyr::select(datetime,pH_s_durafet_temp_fb)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(pH_s_durafet_temp_fb = mean(pH_s_durafet_temp_fb, na.rm = T))

#  make means in "d" to have same format and call it "discrete"
discrete <- d %>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(sal_fb = mean(sal_fb, na.rm = T),
                   temp_fb = mean(temp_fb, na.rm = T),
                   at_mean_interp = mean(at_mean_interp, na.rm = T),
            at = mean(at, na.rm = T),
            qflag_at = mean(qflag_at, na.rm = T),
            ct_mean_interp = mean(ct_mean_interp, na.rm = T),
            ct = mean(ct, na.rm = T),
            qflag_ct = mean(qflag_ct, na.rm = T)
            )
# join discrete + seafet/durafet
discrete <- left_join(discrete, pH_seafet_mean, by='datetime')
discrete <- left_join(discrete, pH_durafet_mean, by='datetime')

##   *****Attention, temp noted by logisticians in d is FB temp with SBE45 ******
##   *****Attention, I asked to the logisticians to log insitu temp from 9 june 2019

@@

discrete_no_na <- discrete %>%
  dplyr::filter(!is.na(sal_fb)  & !is.na(temp_fb) & !is.na(at) & !is.na(ct))
discrete_is_na <- discrete %>%
  dplyr::filter(is.na(sal_fb)  | is.na(temp_fb) | is.na(at) | is.na(ct))

carb <- carb(15, discrete_no_na$at*1e-6, discrete_no_na$ct*1e-6,S=discrete_no_na$sal_fb, T=discrete_no_na$temp_fb, P=0, Pt=0, Sit=0,k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")

discrete_no_na$phcalc<- carb$pH
discrete_no_na$pco2calc<- carb$pCO2

#create new variable in "discrete_is_na" to bind "discrete_no_na"
discrete_is_na$phcalc<- NA
discrete_is_na$pco2calc<- NA
discrete <- rbind(discrete_no_na, discrete_is_na)
discrete%>%dplyr::arrange(datetime)
```

```{r Combine discrete and continous data, echo=FALSE}

# at
closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
discrete$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
# remove the drop_na() because of seafet/durafet line with na
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, at, qflag_at) %>%
    dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

# seaFET pH 
# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
# discrete$closest_datetime <- d_all$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pH_s_seafet_temp_ctd) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")
# #voltINT
# discrete2merge <- discrete %>%
#   #drop_na() %>%
#   dplyr::select(closest_datetime, voltINT) %>%
#   rename(datetime=closest_datetime)
# d_all <- full_join(d_all, discrete2merge, by="datetime")
# #voltEXT
# discrete2merge <- discrete %>%
#   #drop_na() %>%
#   dplyr::select(closest_datetime, voltEXT) %>%
#   rename(datetime=closest_datetime)
# d_all <- full_join(d_all, discrete2merge, by="datetime")

# duraFET pH 
# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
# discrete$closest_datetime <- d_all$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pH_s_durafet_temp_fb) %>%
  dplyr::filter(!is.na(closest_datetime)) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

@@

sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd)

@@

dygraph(sal_xts, group = "awipev", main="Salinity (in situ CTD)", ylab="Salinity") %>%
      dySeries("sal_insitu_ctd", color = "blue", strokeWidth = 0, label = "S") %>%

@@

temp_insitu_xts <- dplyr::select(d_all, datetime, temp_insitu_11m)

@@

      dySeries("temp_insitu_11m", color = "blue", strokeWidth = 0, label = "T") %>%

@@

durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_fb)

@@

    dySeries("pH_s_durafet_temp_fb", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%

@@

seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_ctd)

@@

dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ T CTD)", ylab="pHT") %>%

@@

  dySeries("pH_s_seafet_temp_ctd", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%

@@

# at_contros_cleaned_xts <- dplyr::select(d_all, datetime,sal_fb,sal_insitu_ctd)
# at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
# dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
#    #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
#   #dySeries("AT_filtered2", color = RColorBrewer::brewer.pal(4, "Set2"), strokeWidth = 0, pointSize=2) %>%
#   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
#   dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2)

# date format into charactere
d_all$datetime_chr <- as.character(d_all$datetime)

p_sal_fb_ctd<-  ggplot(d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),aes(x=sal_insitu_ctd, y= sal_fb, label = month))+
  geom_point( aes(color=factor(datetime_chr))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  #geom_line(aes(x = sal_fb, y = sal_fb), linetype = "dashed") +
  geom_abline(slope=1, intercept=0, linetype = "dashed")+
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
  labs(title = paste("","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + #
  coord_fixed(ratio = 1 )+
   scale_colour_discrete(guide="none") +
  labs( x="Salinity CTD > 8 m", y="Salinity FB ", color = "Months") +theme_bw()

print(p_sal_fb_ctd)

@@

### Plotly
# p_p_sal_fb_ctd <- ggplotly(p_sal_fb_ctd,dynamicTicks = TRUE)
# filename.html <- paste0("p_p_sal_fb_ctd.html")
# saveWidget(p_p_sal_fb_ctd, filename.html, selfcontained = T, libdir = "lib")

# # PLOT
seafet_contros_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd, sal_fb, sal_mix)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="Salinities", ylab="PSU") %>%
dySeries("sal_insitu_ctd", label = "sal_insitu_ctd", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
dySeries("sal_fb", label = "sal_fb", color ="blue",axis= "y2", strokeWidth=0, pointSize=4) %>%
dySeries("sal_mix", label = "sal_mix", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
#dySeries("pressure_insitu_ctd_filtered", label = "pressure_insitu_ctd_filtered", color ="black", strokeWidth=0, pointSize=2) %>%
  dyLegend(show = "onmouseover")   %>%
  #dyAxis( "y2",valueRange = c(-3, 36))%>%
  dyAxis( "y2",valueRange = c(25, 36))%>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)

@@

p_temp_11_fb<-  ggplot(d_all,aes(x=temp_insitu_11m, y= temp_fb, label = month))+
  geom_text( aes(color=factor(datetime_chr))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("T FB vs T 11 m","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
  labs( x="T 11 m", y="T FB ", color = "Months")  +theme_bw()
print(p_temp_11_fb)

d_all$diff_T_fb_11m <- d_all$temp_fb - d_all$temp_insitu_11m
mean_diff_T_fb_11m <- round(mean(d_all$diff_T_fb_11m, na.rm = TRUE), digits = 2)
sd_diff_T_fb_11m <- round(sd(d_all$diff_T_fb_11m, na.rm = TRUE), digits = 2)

### Plotly
# p_p_temp_11_fb <- ggplotly(p_temp_11_fb,dynamicTicks = TRUE)
# filename.html <- paste0("p_p_temp_11_fb.html")
# saveWidget(p_p_temp_11_fb, filename.html, selfcontained = T, libdir = "lib")

The mean difference between temperature Ferrybox and in situ at 11 m is: `r mean_diff_T_fb_11m` ± `r sd_diff_T_fb_11m`°C.

@@

p<-  ggplot(d_all,aes(x=temp_insitu_ctd, y= temp_insitu_11m, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("T CTD > 8 m vs T 11 m","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
  labs( x="T CTD > 8 m", y="T 11 m ", color = "Months")  +theme_bw()
print(p)

d_all$diff_T_ctd_11m <- d_all$temp_sf - d_all$temp_insitu_ctd
mean_diff_T_ctd_11m <- round(mean(d_all$diff_T_ctd_11m, na.rm = TRUE), digits = 2)
sd_diff_T_ctd_11m <- round(sd(d_all$diff_T_ctd_11m, na.rm = TRUE), digits = 2)
```

The mean difference between temperature Ferrybox and in situ at 11 m is: `r mean_diff_T_ctd_11m` ± `r sd_diff_T_ctd_11m`°C.

@@

# # We decided to calibrate pH data within each pH spectro measurement.
# # Thus, each pH spectro is taken as one calibration periode. 
# # We calculate here the day between 2 pH spectro in order to have the start/end of one deployment period.
# sfPeriod <- d_all%>%
#   dplyr::select(datetime, pH_s_seafet_temp_ctd)%>%
#   dplyr::filter(!is.na(pH_s_seafet_temp_ctd))
# # Remove pH spectro that not allow a calibration because of missing calibration value (voltINT, Sal or Temp insi)
# sfPeriod <- sfPeriod%>%
# dplyr::filter(datetime != "2018-04-16 07:00:00" & datetime != "2018-12-14 09:00:00" & datetime != "2019-01-18 09:00:00")
# 
# sfPeriod <-  sfPeriod %>%
#   dplyr::arrange(datetime) %>%
#   dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(sfPeriod)])/2* 3600)))%>%
#   dplyr::mutate(sf_interval = datetime + middle[2:nrow(sfPeriod)])
# 
# #put interval in a list with the start date of seaFET measurements
# sfinterv <- c( as_datetime("2017-08-24 13:00:00"), sfPeriod[,4])
# #Change period sfinterv[5]. make the end of this period longer until 2018-03-21 23:59:00 
# # This is needed in order to take in consideration pH from March 2018 with a calibration E0 lower (-1.4) than the next period (-0.38).
# sfinterv[5] <- ymd_hms("2018-03-22 23:59:59")
# #  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
# # sfinterv[6] <- ymd_hms("2018-04-24 18:00:00")
# #  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
# # sfinterv[14] <- ymd_hms("2019-01-29 16:00:00")
# 
# #sfinterv <-sort(unlist(sfinterv, use.names=FALSE))
# # set deployment period between 2 spectro measurements.

@@

####
## calculation of E0INT25/E0EXT25 ##
##     new sf_calib function      ##
####
calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$pH_s_seafet_temp_ctd,
                          calT = d_all$temp_insitu_ctd, calSal = d_all$sal_insitu_ctd )
# put number of deployment 
calib_spectro$deployment_sf <- d_all$deployment_sf
